\documentclass{my_cv}
\usepackage[skins]{tcolorbox}
\begin{document}


\begin{multicols}{2}[
    \titletext{Ansel}%
        {Boero}%
        {Mathematician \& Data Engineer}%
        {boeroansel@gmail.com}%
        {+393484426258}%
        {\href{https://github.com/anselboero}{GitHub}}%
        {\href{https://anselboero.com}{Personal Blog}}%
]
\end{multicols}


\section{\faFileText}{SUMMARY}
Passionate about different fields, I have developed skills in multiple disciplines, which allows me to approach problems through diverse lenses and optimize the quality of proposed solutions. In particular, the analytical rigor provided by a theoretical mathematics background, combined with extensive practical experience as a Data Engineer, provides a solid foundation for addressing the complex challenges of the modern data world, such as Data Modeling (with solid knowledge about Finance and Payments Industry), Data Architecture, Software Engineering, and Orchestration. 


\noindent
\hrulefill


\begin{multicols}{2}

\setlength{\columnseprule}{0.2pt}

\section{\faList}{SKILLS \& INTERESTS}

\subsection{Computer}

\textbf{Languages (professional):} Python, SQL \\ %
\textbf{Other languages:} JavaScript, Scala \\ %
\noindent\textbf{Tools:} Git, DBT, Airflow, Dagster, Looker \\ %
\noindent\textbf{Main databases:} BigQuery, Impala, PostgreSQL \\%
\noindent\textbf{Other interests:} Data Modeling, Data Structures, Linux, DDD, Cloud (GCP and AWS, mainly), Open Source, Blockchain  %

\subsection{Quantitative}

Analysis, Game Theory, Logic, Probability Theory.

\subsection{Other Interests}
Music (professional piano player), writing, cognitive sciences \& critical thinking, personal finance, Payments Industry, Bouldering, Running and Calisthenics, charity (donating 10\% of net salary since 2022). 


\subsection{Languages}

\textbf{English:} C1, IELTS 7.0 (2024) \\ %
\noindent\textbf{German:} A2, currently studying it \\ %
\noindent\textbf{Italian:} native \\ %

\noindent
\hrulefill

\section{\faGraduationCap}{EDUCATION}

\school{Mathematics, BSc / \href{https://en.unito.it/}{UniTo} / 2015 - 2019} %
{Turin, IT } %
{Algebra, Analysis, Geometry, Mathematical modeling.} %
{Homomorphic Encryption}%
{Prof. \href{https://sites.google.com/view/cristinabertone/home}{Cristina Bertone}, PhD.}%


\columnbreak

\section{\faPencil}{WORK}

\work{Analytics Engineer / 2023 - ongoing}%
    {Vinted - Payments Domain / Berlin, DE}%
    {\textbf{Modeling, development, and maintenance of the new Vinted Pay Data Platform}\\
    In 2023, Vinted was granted with an \href{https://www.lb.lt/en/news/electronic-money-institution-licence-granted-to-a-subsidiary-of-vinted}{EMI license} and has since been developing and testing PSP-Like services. The Vinted Pay Data Warehouse aims to produce both internal and external reports for local and European financial institutions, and supporting business operations through key metrics development.\\
    \textbf{Development and Ownership of the Cost Control Project}\\
    The main objective is tracking costs associated with payment services (Pay-Ins, Payouts, KYC, Chargebacks, Tokenizations) per transaction. this solution can break down costs by various dimensions, such as Fee Type, Payment Method, Country Code, and Payment Provider\\
    This project is crucial in two main areas: Monthly Reconciliation and business support, particularly for the Payments Orchestration team. \\ \\
    Main Results:
    \begin{itemize}
      \item   From Invoice Level to Transaction Level Costs: stronger and deeper insights.
      \item Full automation of payment reconciliation, reducing probability of error and enabling resource allocation to more significant projects.
      \item Discovery of bugs in PSPs, achieving €50k in savings and €70k in reimbursements.
    \end{itemize}
    \textbf{Support to Payments Data Migration} \\
    Vinted has been migrating to the Cloud its data stack. I have supported the migration of KYC and Pay-ins models. Vinted has been migrating to the Cloud its data stack. I have supported the migration of KYC and Pay-ins models.\\}%
    {\keyword{BigQuery}\keyword{Dbt}\keyword{Airflow}\keyword{Python}\keyword{Looker}\keyword{GIT}\keyword{Data Mesh}\keyword{Data Management}\keyword{Payments Business}}%

\work{Data Consultant / 2021 - 2023}%
    {NNIT / Germany, Remote}%
    {Consultant in Life Science \& Pharma industry. Main Companies: Boehringer Ingelheim, Eli Lilly, Bayer.\\ \\
    \textbf{\href{https://www.nnit.com/our-solutions/regulatory-affairs/aura-x/}{Aura-X}: Automated Regulatory Extraction}\\
    Extracting relevant information from SMPC documents (mainly PDFs) and matching with RMS vocabularies using NLP and LLMs.
    Internal Product: Developed NLP models, data architecture, and a web interface used by the experts team to validate results obtained from NLP algorithms.\\
    \textbf{Support to Data Migrations}\\}%
{\keyword{Python}\keyword{Airflow}\keyword{Flask}\keyword{Pandas \& Spacy}\keyword{Data Quality}\keyword{Agile}}%
\work{Analyst Consultant / 2020 - 2021}%
    {Capgemini - Insight \& Data / Milan, IT}%
    {Consultant in Financial Industry.\\ \\
    \textbf{Data Migration}\\
    Data Migration for an Italian banking Company (BPER BANCA). My work was mainly focused on Data Quality Processes.\\}%
{\keyword{OracleSQL}\keyword{Informatica}\keyword{Python}\keyword{Tableau}\keyword{Denodo}\keyword{Consultancy}}%


\end{multicols}
\end{document}
